European or American? A re-examination of the transatlantic influence over the IMF

### 2025-07-16 manuscript/manuscript.qmd
Add european recipient coefficient interpretation

>>>>

Furthermore, the `European recipient` variable itself is associated with *less favourable* outcomes, even after controlling for ties to the US and European powers, as well as other covariates. This negative association is statistically significant at the 5% level for both the loan-to-GDP ratio and the number of IMF conditions. These results suggest that, on average, European countries tend to receive *less favourable* treatment from the IMF than non-European countries, despite their typically stronger connections to Western European powers.
